# Practical Machine Learning programming Assignment

This document illustrates the fitting of a random forest model to predict the activity quality from sensor data. 

Load required packages and data
```{r}
library(dplyr)
library(caret)
set.seed(123)
train <- read.csv("pml-training.csv",header=TRUE,stringsAsFactors=FALSE)
test <- read.csv("pml-testing.csv",header=TRUE,stringsAsFactors=FALSE)

```

Select features with no missing values;
```{r}
selectedFeatures <- complete.cases(t(test))
selectedFeatures[2:7]<-F # remove time and subject variables
train <- train[,selectedFeatures]
test<- test[,selectedFeatures]
test <- test[,-ncol(test)]
train$classe <- factor(train$classe)
```

Split training set to a training and validation set:
```{r}
inTrain <- createDataPartition(train$classe,p=0.7,list=F)
train <- train[inTrain,]
val <- train[-inTrain,]
```

Train a random forest with 10-fold cross-validation and the default number of values for mtry (3)
```{r,cache=TRUE}
model <- train(classe~.,data=train[,-1],method="rf") #remove id variable from train set
model
```

Test the model on the validation set
```{r}
pred<-predict(model,newdata=val)
mean(pred==val$classe)
```

## Final model accuracy estimates: 

Cross-validation accuracy: 98.9%

Validation set accuracy: 100%

Test set accuracy (20 examples): 100%

```{r, echo=FALSE}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
```

